Modeling and Simulation of Load Balancing Strategies for Computing in High Energy Physics

### 2018-10-09 paper/paper.tex
Update template

\documentclass[a4paper]{jpconf}

@@

\bibliographystyle{iopart-num}

@@

\author{Ren\'e Caspart${}^{1}$,
	Patrick Firnkes${}^{2}$,
	Manuel Giffels${}^{1}$,
	Anne Koziolek${}^{2}$,
	G\"unter Quast${}^{1}$,
	Ralf Reussner${}^{2}$, 
	Maximilian Stemmer-Grabow${}^{2}$}

\address{
	${}^{1}$Institute for Experimental Particle Physics (ETP) \\
	${}^{2}$Institute for Program Structures and Data Organization (IPD) \\
	at Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany}

\ead{koziolek@kit.edu}

\begin{abstract}
	The amount of data to be processed by experiments in high energy physics (HEP) is tremendously increasing in the coming years. To cope with this increasing load, most efficient usage of the resources is mandatory. Furthermore, the computing resources for user jobs in HEP will be increasingly distributed and heterogeneous, resulting in a more difficult scheduling due the increasing complexity of the system. 
	We aim to create a simulation for the WLCG helping the HEP community to solve both challenges: a more efficient utilization of the grid and coping with the rising complexity of the system.
	There is currently no simulation existing helping the operators of the grid to make the correct decisions while optimizing the load balancing strategy.

@@

	Finally, the simulation results are validated using real word performance data. Our results suggest that simulating larger parts of the grid is feasible and can help to optimize the utilization of the grid.
\end{abstract}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{images/resources}
	\caption[]{Estimated CPU resources of ATLAS \cite{community}}
	\label{resources}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.55\linewidth]{images/process}
	\caption[]{The Simulation Process}
	\label{process}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{images/seff}
	\caption[]{Model of Job Behaviour}
	\label{seff}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale = 0.6]{images/shares}
	\caption[]{Measured and Simulated Shares of Job Types}
	\label{shares}
\end{figure}

@@

\begin{figure}[h]

@@

	};
	\addlegendentry{Measured (average)};
	\addlegendentry{Simulated};
	\end{axis}
	\end{tikzpicture}
	\caption[]{Measured and Simulated CPU Efficiency}
	\label{utilization}
\end{figure}

@@

This proof of concept showed that an automated model parameter extraction and model creation is possible and that Palladio can be used to evaluate load balancing strategies for computing in HEP. In contrast to the existing simulations our simulation models a site in a more detailed way, enabling the evaluation of load balancing strategies on working node level. The next step is the evaluation of design decisions mentioned in \Cref{outlook}.
\section*{References}
\bibliography{paper}

>>>>

\documentclass{webofc}
\usepackage[varg]{txfonts}

@@

@@

\author{
	\firstname{Ren\'e} \lastname{Caspart}\inst{1} \and
	\firstname{Patrick} \lastname{Firnkes}\inst{2} \and
	\firstname{Manuel} \lastname{Giffels}\inst{1} \and
	\firstname{Anne} \lastname{Koziolek}\inst{2}\fnsep\thanks{\email{koziolek@kit.edu}} \and
	\firstname{G\"unter} \lastname{Quast}\inst{1} \and
	\firstname{Ralf} \lastname{Reussner}\inst{2} \and
	\firstname{Maximilian} \lastname{Stemmer-Grabow}\inst{2}
}

\institute{
	Institute for Experimental Particle Physics (ETP) 
	\and
   Institute for Program Structures and Data Organization (IPD) \\
	at Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany
}

\abstract{%
	The amount of data to be processed by experiments in high energy physics (HEP) is tremendously increasing in the coming years. To cope with this increasing load, most efficient usage of the resources is mandatory. Furthermore, the computing resources for user jobs in HEP will be increasingly distributed and heterogeneous, resulting in a more difficult scheduling due the increasing complexity of the system. 
	We aim to create a simulation for the WLCG helping the HEP community to solve both challenges: a more efficient utilization of the grid and coping with the rising complexity of the system.
	There is currently no simulation existing helping the operators of the grid to make the correct decisions while optimizing the load balancing strategy.

@@

	Finally, the simulation results are validated using real word performance data. Our results suggest that simulating larger parts of the grid is feasible and can help to optimize the utilization of the grid.
}%
\maketitle
%

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.7\linewidth]{images/resources}
	\caption[]{Estimated CPU resources of ATLAS \cite{community}}
	\label{resources}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.55\linewidth]{images/process}
	\caption[]{The Simulation Process}
	\label{process}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\linewidth]{images/seff}
	\caption[]{Model of Job Behaviour}
	\label{seff}
\end{figure*}

@@

\begin{figure*}[h]
	\centering
	\includegraphics[scale = 0.6]{images/shares}
	\caption[]{Measured and Simulated Shares of Job Types}
	\label{shares}
\end{figure*}

@@

\begin{figure*}[h]

@@

	};
	\addlegendentry{Measured (average)};
	\addlegendentry{Simulated};
	\end{axis}
	\end{tikzpicture}
	\caption[]{Measured and Simulated CPU Efficiency}
	\label{utilization}
\end{figure*}

@@

This proof of concept showed that an automated model parameter extraction and model creation is possible and that Palladio can be used to evaluate load balancing strategies for computing in HEP. In contrast to the existing simulations our simulation models a site in a more detailed way, enabling the evaluation of load balancing strategies on working node level. The next step is the evaluation of design decisions mentioned in \Cref{outlook}.

\bibliography{paper}
